Presentation Exercise

### 2024-07-11 presentation-exercise/presentation-exercise.qmd
Secondary Update of Presentation Exercise

# Plot the data
ggplot(data, aes(x = year, y = cpi_change)) +
  geom_line(color = "#0072B2", size = 1.5) +  # Line plot
  geom_point(color = "#0072B2", size = 3) +   # Points at data points
  geom_text(aes(label = paste0(cpi_change, "%")), vjust = -0.5, hjust = 0.5, color = "#0072B2", size = 4) +  # Labels on points
  scale_x_continuous(breaks = years, labels = years) +  # X-axis labels
  scale_y_continuous(limits = c(0, max(cpi_change) * 1.1), breaks = seq(0, max(cpi_change) * 1.1, by = 1), labels = paste0(seq(0, max(cpi_change) * 1.1, by = 1), "%")) +  # Y-axis labels
  labs(
    title = "Consumer Price Index Change from One Year Earlier",
    x = "Year",
    y = "CPI Change (%)"
  ) +
  theme_wsj(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    axis.title = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 12),
    panel.grid.major.x = element_line(color = "grey90"),  # Gridlines
    panel.grid.minor.x = element_blank(),  # Minor gridlines
    panel.grid.major.y = element_line(color = "grey90")
  )

@@

# Plot the heatmap
ggplot(data, aes(x = month, y = category, fill = percentage_change)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#1A9641", midpoint = 0, limits = c(-10, 10), name = "Percentage Change (%)") +
  geom_text(aes(label = paste0(percentage_change, "%")), size = 3, color = "black") +
  labs(
    title = "Year-over-Year Price Changes for Major Categories of Goods",
    subtitle = "Data as of June 12, 2024\nAll items are percentage change from a year earlier",
    x = "Month",
    y = "Category"
  ) +
  theme_classic(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 16, face = "bold"),
    legend.title = element_text(size = 14, face = "bold"),
    legend.text = element_text(size = 12)
  )

>>>>

# Plot the data
ggplot(data, aes(x = year, y = cpi_change)) +
  geom_line(color = "#0072B2", size = 1.5) +  # Line plot
  geom_point(color = "#0072B2", size = 3) +   # Points at data points
  geom_text(aes(label = paste0(cpi_change, "%")), vjust = -0.5, hjust = 0.5, color = "#0072B2", size = 4) +  # Labels on points
  scale_x_continuous(breaks = years, labels = years) +  # X-axis labels
  scale_y_continuous(limits = c(0, max(cpi_change) * 1.1), breaks = seq(0, max(cpi_change) * 1.1, by = 1), labels = paste0(seq(0, max(cpi_change) * 1.1, by = 1), "%")) +  # Y-axis labels
  labs(
    title = "Consumer Price Index Change from One Year Prior",
    x = "Year",
    y = "CPI Change (%)"
  ) +
  theme_wsj(base_size =1) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    axis.title = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 12),
    panel.grid.major.x = element_line(color = "grey90"),  # Gridlines
    panel.grid.minor.x = element_blank(),  # Minor gridlines
    panel.grid.major.y = element_line(color = "grey90")
  )

@@

# Plot the heatmap
ggplot(data, aes(x = month, y = category, fill = percentage_change)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#1A9641", midpoint = 0, limits = c(-10, 10), name = "Percentage Change (%)") +
  geom_text(aes(label = paste0(percentage_change, "%")), size = 1, color = "black") +
  labs(
    title = "Year-over-Year Price Changes for Major Category of Goods",
    subtitle = "Data as of June 12, 2024\nAll items are percentage change from a year earlier",
    x = "Month",
    y = "Category"
  ) +
  theme_classic(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 16, face = "bold"),
    legend.title = element_text(size = 14, face = "bold"),
    legend.text = element_text(size = 12)
  )
